
\section*{Pools}
\DefineNamedColor{named}{eclipsered}{rgb}{0.686,0.066,0.482}
\definecolor{tablecolor}{named}{eclipsered}


\begin{eptable}{ l | X }
   \epheader{2}{Pool \& Linked Aptitudes}
   Insight & Cognition \& Intuition.\\
   Vigor & Reflexes \& Somatics.\\
   Moxie & Savvy \& Willpower.\\
   Flex & Any test.\\
\end{eptable}

Pools may only be used for their linked aptitudes.

\bigskip

\begin{eptable}{ l | X }
   \epheader{2}{General Pool Usage}
    Before Roll & Ignore all modifiers to the test.\\
    Before Roll & Add \modifier{+20} to the test’s target number.\\
    After Roll & Flip-flop dice, e.g. \num{83} becomes \num{38}.\\
    After Roll & Upgrade success to superior, or superior to 2x superior.\\
    After Roll & Downgrade critical failure to regular failure.\\
    Ongoing & Get \modifier{+5} (\SI{1}{pt}) / \modifier{+10} (\SI{2}{pts}) for apt' linked skill tests for \SI{24}{h}.\\
\end{eptable}

Skill boosting can only be done by permissible pool. Boosting
only boosts \textit{one} aptitude, not both!

\bigskip



\begin{eptable}{ X }
   \epheader{1}{Insight}
   Go first one turn when only mental / mesh actions taken.\\
   Take 1 extra complex (or 2 quick) mental actions.\\
   Acquire clue through investigation, insight or analysis.\\
\end{eptable}

If multiple people attempt to go first, all the ones that go first
again go by initiative. Extra actions happen after all other characters
could act this turn.

\bigskip



\begin{eptable}{ X }
   \epheader{1}{Vigor}
   Go first in an action turn.\\
   Take 1 extra complex (or 2 quick) physical actions.\\
   Ignore effects of \num{1} wound for \SI{24}{h}.\\
\end{eptable}

If multiple people attempt to go first, all the ones that go first
again go by initiative. Extra actions happen after all other characters
could act this turn.

\bigskip

\begin{eptable}{ X }
   \epheader{1}{Moxie}
   Ignore effects of \num{1} trauma for \SI{24}{h}.\\
   Avoid making infection test.\\
   Negate a player’s social gaffe that the character wouldn’t make.\\
   Refresh minor (\SI{1}{pt}) or moderate network favor (\SI{2}{pt}).\\
   Acquire clue through social interaction w/o needing test.\\
\end{eptable}




\bigskip



\begin{eptable}{ X }
   \epheader{1}{Flex}
   Introduce NPC to scene. Define \textit{one} aspect (\eg, morph, faction, skill).\\
   Introduce minor non-weapon item or clue to scene. GM determines placement.\\
   Introduce environmental factor (\eg., cover, hiding, distractions, shelter).\\
   Introduce loose or minor relationship with NPC.\\
\end{eptable}

All introductions must be \textbf{plausible}! Generally player
can define one aspect, GM defines rest.

\bigskip


\begin{eptable}{ l | X }
   \epheader{2}{Refreshing}
   Short (2 per \SI{24}{h}) & Takes \SI{10}{min}, restores \dice{1d6} points.\\
   Long (1 per \SI{24}{h}) & Takes \SI{4}{h}, restores all pools.\\
\end{eptable}

\begin{itemize}
    \itembox Refreshing requires uninterrupted rest with only minimal activity.
    \itembox Resting also reduces Infection Rating (\modifier{-10} on short rest), or resets it altogether (long rest).
\end{itemize}
