
\begin{multicols}{2}

\section*{General GM Tips}
\section*{Fantasy Tropes in Eclipse Phase}


\eclipsephase can be daunting to GM at first, in particular when coming from a fantasy background.
%
Many \textit{tropes} require different game play elements to produce similar results.
%
Here are some tips to convert some of them to the \eclipsephase universe.

\medskip

For example:
``The heroes travel along a lonely road through the forest.
They find the remains of an ambush site.
A wounded survivor tells them a princess was captured by an evil mage and is kept in an old tower.
Being too far away from the next town to call for help, he urges the players to rescue her.
The players sneak into his evil tower, fight the mage, and eventually rescue the princess.
They are being handsomely rewarded.``

In the \eclipsephase:

\end{multicols}

\begin{tabletwo}{Adapting Tropes to \eclipsephase}
    Bandits & Gang (A, B). Pirates (X, Y, Z). Conflicting Faction (Brinkers, X). Spies (Jovian Republic).\\
    Monster Encounters & Automated Security Systems (X). AI (various morphs). Gamma Forks. (Not-quite) Uplifts. Infected (X-Risks). Nano swarms.\\
    Ambush & xxx \\
    Nature \& Forest & Rock Formations. Terraformed Micro Climate. Stations. Hydroponics. Parks. Exoplants. Derelict Station Parts. \\
    Pacing & Generally `one order of magnitide` faster in \ep (weeks become days, days become hours). \textit{Three days in dungeon} becomes \textit{3 hours in old ventilation system}.\\
    Succeeding \& Failing & Related to Pacing. If players have time, they will (should reasonably) succeed. Implication: In many cases \textit{adventure} / challenge only arises if there is less time than needed. \\
    Being Lost & Actually Lost (away from civilization, unknown habitat). Factually Lost (recently reworked structure, unknown / moving target) \\
    Maps & Available except special events (major disaster, very old station part, Earth, Exoplanet). \\
    Being Alone & Totally Alone (interference, radio transmitter outside Mesh range, Exoplanet). Physically Alone (help takes too long to arrive).\\
    Exploring the Dungeon & Derelict Ships. Old Station Parts. Earth. Exoplanet Ruins. Habitats w/o Clearance (\eg, gang territory, private dwellings).\\
    Resting \& Healing & Morph damage only scary w. tight pacing (timeframe hours). Ego damage much more severe (timeframe weeks). Also remember to apply hardening (permanent)! \\
    Death & Regular death in \ep needs additional story consequences (\eg, target escaped, Stack popped by enemy, too late for rendezvous, exoplanet and no spare morphs left)! \\
    Death (Final) & Exurgent Virus (the ultimate threat: use sparingly, loses edge).\\
    Murder Plots & Depends on victim stratum (rich: usually had good backup, middle class: also required popped stack and no backup, very low or Jovian: might be dead for real). \\
    Kidnapping & Becomes Forknapping. Often more scary than murder. \\
    Sneaking & Situation dependent. Alternatively Blend In (passcoes)  \\
    Magic & Infosec (Hacking, AR) . Military Technology. AGIs. Exsurgent Virus. Asyncs. \\
    %Vendors \& Items & . \\
    Gold \& Rewards & Information (multi-use blueprints, single-use expensive). Reputation. Contacts. Restricted Items (weapons, weapon blueprints). Morphs. Apartments. Vehicles. Ships.\\
    %Heroism & Must be agreed out-of-game. Firewall implies certain heroism. \\
    The Princess &  \\
\end{tabletwo}
