
\section*{Actions}
\DefineNamedColor{named}{eclipsered}{rgb}{0.886,0.566,0.482}
\definecolor{tablecolor}{named}{eclipsered}


\begin{eptable}{ X }
   \epheader{1}{Asphyxiation}
   Holding breath: \SI{2}{min} (less when stressed). \\
   For each \SI{30}{s} longer, \skill{SOM} with cumulative \modifier{-10}. \\
   When fail: unconscious, treated as DV = DUR, \num{10} more DV per minute.\\
   Every \SI{30}{s} \skill{WIL} or \sv{1d6} and unable to act, and \skill{WIL} to non-rescue action. \\
\end{eptable}

\bigskip

\begin{eptable}{ l | X}
   \epheader{2}{Falling}
   1 - 2 meters & \dv{1d10}.\\
   3 - 5 meters & \dv{2d10}.\\
   6 - 8 meters & \dv{3d10}.\\
   Over 8 meters & +1 per meter.\\
\end{eptable}

\bigskip


\begin{eptable}{ X }
   \epheader{1}{Fire}
   Burning characters and objects \dv{1d6} per round (saved by Energy Armor). \\
   Armor may catch fire though. \\
   Fire increases every \num{5} turns (to \dv{1d10}, \dv{2d10}, \dv{3d10}, +5, +10, ...). \\
   Water \& co. might reduce this. \\
\end{eptable}

\bigskip

\begin{eptable}{ X }
   \epheader{1}{Gravity}
   For characters not used, up to \num{3} day to accustom to new Gravity.\\
   During that time \modifier{-10} to social, physical, \modifier{-20} combat, fine motorics.\\
\end{eptable}

\bigskip

\begin{eptable}{ l | X}
   \epheader{2}{Atmosphere}
   Contamination & From  \modifier{-10} to  \modifier{-30}.\\
   Dangerous & Same as Contamination plus appropriate effects.\\
   High-Pressure & Same as Contamination plus appropriate effects.\\
   Toxic & Up to \dv{2d10} per turn if not holding breath.\\
   Corrosive & \dv{1d10} per turn, regardless of holding breath. Dmg. items.\\
   Decompression & \skill{REF} or blown out, \skill{SOM} or let go. Fray or debris hit.\\
   Extreme & Usually kills quickly.\\
   Radiation & No actual rules, apply common sense.\\
   Underwater & General \modifier{-20} for actions performed underwater.\\
   Vacuum & See Asphyxiation, if Vacuum Sealing \SI{1}{min} extra time.\\
   Space & See Vacuum. No thermal protection \modifier{-10} and \dv{2} per min.\\
\end{eptable}
